Monte Carlo tree search compared to A\(^*\) in airspace configuration decision problem

### 2018-05-15 article/article.tex
(+) Scenario
(+) Abstracted

\begin{abstract}
  A nice abstract
\end{abstract}

@@

Currently, configuration is mainly decided on the fly by chief officer (TODO).
This decision is based on the actual workload on each position. In this
approach, future workload estimation is based on the controller's feelings and
it therefore lacks a workload prediction tool.
This papers aims at providing this tool as well as a method offering a smoother
workload during the day.

@@

TODO : meilleure explication des transitions?

@@

>>>>

\begin{abstract}
  Dynamic airspace configuration falls under highly combinatorial partitioning
  problems. Since exact methods tend to be overwhelmed by the complexity of such
  problems, a stochastic approach is here considered. This paper presents the
  the Monte Carlo tree search algorithm using UCT search and adapted to one
  player games. The application of the algorithm to the airspace partitioning is
  then detailed. Finally the Monte Carlo tree search is compared to the A\(^*\).
\end{abstract}

@@

Currently, configuration is mainly decided on the fly by chief officer.
This decision is based on the actual workload on each position. In this
approach, future workload estimation is based on the controller's feelings and
it therefore lacks a workload prediction tool.
This papers aims at providing this tool as well as a method offering a smoother
workload during the day.

@@

@@

The traffic is simulated the following way, each elementary module has an
associted list which, at index \(i\) has the number of aircraft in it at time
step \(i\). Thoses lists has been randomly generated. The set of lists form a
scenario which is used in all following tests.
